Hector Permafrost

### 2019-02-06 analysis/paper/paper.Rmd
Add lots of methods notes to paper

@@

@@

>>>>

## Parameter calibration

We used the `BayesianTools` R package [@R-BayesianTools] for all parameter calibration.
The outputs of these calibrations are joint posterior distributions of parameters and their covariances, from which we sample for the sensitivity analysis.

For global parameters, we used the following likelihood:

$$ \log(L) = \sum_s Normal(Hector(\Beta, Q_{10}, s) | CMIP5(s), \sigma) $$

where $s$ is one of the four representative carbon pathways (RCPs), $CMIP5(s)$ are the CMIP5 global mean outputs for the corresponding variables, and $\sigma$ is the model error (estimated during the fit).
We also used the resulting distributions for $\Beta$ and $Q_{10}$ for the non-permafrost biome in cases 2 and 3.
We feel this is appropriate because the CMIP5 models against which these parameters are calibrated do not include permafrost C feedbacks.

For case 2, we calibrated the permafrost-specific $\Beta$ and $Q_{10}$ against various literature sources, including:

- Land surface model simulations [@hope_2015_economic; @schaefer_2011_amount; @burke_2017_quantifying].
    - Try to calibrate against NPP and soil respiration if possible
- Literature surveys [@schaefer_2014_impact] 
- Warming experiments [@wickland_2006_effects]
- TODO: Others?

Some of these are time series, while others are individual estimates at particular points in time.
To give them equal weight in the likelihood, we down-weight the time series likelihoods by the number of time steps.

We derived a distribution for the Arctic warming factor from TODO.

TODO: Table and multi-panel figure of input datasets.

For the $\alpha$ and $\phi$ parameters in case 3, we looked at the literature on permafrost methane emissions [e.g., @wickland_2006_effects].

## Initial conditions

For case 1, we use the Hector defaults [@hartin_2015_simple].

For cases 2 and 3, we assumed the same total pool sizes as case 1, but divided them into the permafrost and non-permafrost biomes according to TODO.

@@

Other Hector parameters to consider.

| Variable | INI name | Description                                 | Value |
|----------|----------|---------------------------------------------|-------|
| $f_{nv}$ | `f_nppv` | Fraction of NPP C transferred to vegetation | 0.35  |
| $f_{nd}$ | `f_nppd` | Fraction of NPP C transferred to detritus   | 0.60  |
| $f_{nd}$ |          | Fraction of NPP C transferred to soil       | 0.05  |
| $f_{lv}$ | `f_lucv` | Fraction of LUC change flux from vegetation | 0.10  |
| $f_{ld}$ | `f_lucd` | Fraction of LUC change flux from detritus   | 0.01  |
| $f_{ls}$ |          | Fraction of LUC change flux from soil       | 0.89  |
| $f_{ds}$ |          | Fraction of detritus C that goes to soil    | 0.60  |
| $f_{rd}$ |          | Fraction of respiration C to detritus       | 0.25  |
| $f_{rs}$ |          | Fraction of respriation C to soil           | 0.02  |

According to [@hartin_2015_simple], these were selected to be "generally consistent with previous simple earth system models [e.g., @meinshausen_2011_emulating]".

@@

**Figure**: Parameter distributions from calibration.

**Figure**: Hector projections of parameter sensitivity (CI ribbon, or light/transparent lines), colored (faceted?) by case.

**Figure**: PEcAn-like variance decomposition of parameters (for each parameter: sensitivity, uncertainty, and partial variance)
